Predicting Audio Features with Last.fm Tags

### 2023-03-19 paper/main.tex
add input data tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Departamento de Sistemas Informáticos, Universidad de Castilla - La Mancha, Spai

@@

\abstract{
    In this paper, we discuss a number of experiments to analyze the
    suitability of music label representations to predict certain audio features,
    such as danceability, loudness, or acousticness...
}

@@

Additionally, the Spotify audio features...

@@

\textcolor{red}{To be Continued...}

@@

@@

\subsection{Models}

@@

\bibliography{sn-bibliography}% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{\dots} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\abstract{
    In this paper, we discuss a number of experiments to analyze the
    suitability of music label representations to predict certain audio features,
    such as danceability, loudness, or acousticness \dots 
}

@@

Additionally, the Spotify audio features \dots

@@

\textcolor{red}{To be Continued \dots }

@@

\subsection{Formatting Input Data for Predicting From Last.fm Tags}

The input data passed to the XGBoost regressor is formatted in tabular format, as follows:

\begin{itemize}
      \item Given that $Tags_{k}$ is the set of most $k$ frequent Last.fm tags in the user listening history
            and, where each $tag \in Tags_{k}$.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{tag}$ is the strengh of $tag$ for $track$. This value is in the $0-100$ range.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

An example of this data format is provided in table \ref{tabular_tags_format}.

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Tabular data format for Last.fm tags in XGBoost and Bayesian regressors}\label{tabular_tags_format}%
      \begin{tabular}{@{}lllllll@{}}
      \toprule
      Track                         & $X_{electronic}$ & $X_{ambient}$ & $X_{\dots}$ & $y_{energy}$ & $y_{valence}$ & $y_{\dots}$ \\
      \midrule
      Massive Attack - Blue Lines   & 62               & 6             &  \dots      & 0.496        & 0.947         & \dots  \\
      The Beta Band - Squares       & 40               & 3             &  \dots      & 0.446        & 0.507         & \dots  \\
      \dots                         & \dots            & \dots         &  \dots      & \dots        & \dots         & \dots  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

\subsection{Formatting Input Data for Predicting From Tokens}

In this particular case, the $X$ values of the tabular input data are tokens.
These tokens are obtained from passing the a string of concatenated Last.fm tags through a tokenizer.
The formal definition of this data format is as follows:

\begin{itemize}
      \item Given that $X_l$ is the token vocabulary, where $l$ is the maximum vocabulary length.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{n}$ is token found at position $n$, after tokenizing the tags string.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

An example of this data format is provided in table \ref{tabular_token_format}.

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Tabular data format for tokens in XGBoost and Bayesian regressors}\label{tabular_token_format}%
      \begin{tabular}{@{}llllllll@{}}
      \toprule
      Track                         & $X_{0}$ & $X_{1}$ & $X_{2}$ & $X_{\dots}$ & $y_{energy}$ & $y_{valence}$ & $y_{\dots}$ \\
      \midrule
      Massive Attack - Blue Lines   & 101     & 5099    & 6154    &  \dots      & 0.496        & 0.947         &  \dots  \\
      The Beta Band - Squares       & 101     & 4522    & 2600    &  \dots      & 0.446        & 0.507         &  \dots  \\
      \dots                         & \dots   & \dots   & \dots   &  \dots      & \dots        & \dots         &  \dots  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

\subsection{Formatting Input Data for Predicting From Text}

When using transformer models, the input data is a string.
We must represent the Last.fm tags, which are initially in the $(tag name, tag popularity)$ form, to a a string.

After converting to a string, the formal definition of the input data is as follows:

\begin{itemize}
      \item Given that $X$ is tags represented as text.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{n}$ is set of tags for $track$, encoded as a single string.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

An example of this data format is provided in table \ref{text_format}.

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Text data format for tokens in XGBoost and Bayesian regressors}\label{text_format}%
      \begin{tabular}{@{}lllll@{}}
      \toprule
      Track                         & $X$                                   & $y_{energy}$ & $y_{valence}$ & $y_{\dots}$ \\
      \midrule
      Massive Attack - Blue Lines   & "hip hop, chill, bristol, \dots"      & 0.496        & 0.947         & \dots  \\
      The Beta Band - Squares       & "alternative rock, folk, \dots"       & 0.446        & 0.507         & \dots \\
      \dots                         & \dots                                 & \dots        & \dots         & \dots  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

@@

We trained a commonly used machine learning models to predict an audio feature, given the set of tags for a particular track.

\begin{itemize}
      \item Boosted tree regressor \cite{xgboost}
      \item Naive Bayes Regressor \cite{bayesian}
      \item Fine-tuned GPT-2 model
\end{itemize}

\subsection{Boosted Tree Regressor}

We configured the boosted tree regressor model with the following training parameters:

\begin{table}[h]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{xgboosttable}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter               & Value \\
      \midrule
      objective               & reg:squarederror  \\
      base score              & 0.5 \\
      booster                 & gbtree  \\
      colsample bylevel       & 1 \\
      colsample bynode        & 1 \\
      colsample bytree        & 1 \\
      gamma\footnotemark[1]   & 0 \\
      learning rate           & 0.300000012 \\
      max delta step          & 0 \\
      max depth               & 6 \\
      min child weight        & 1 \\
      estimators              & 200  \\
      n jobs                  & 12  \\
      num parallel tree       & 1 \\
      predictor               & auto  \\
      random state            & 0 \\
      reg alpha               & 0 \\
      reg lambda              & 1 \\
      scale pos weight        & 1 \\
      subsample               & 2 \\
      tree method             & auto  \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Minimum loss reduction required to make a further partition on a leaf node of the tree.}
      \end{minipage}
      \end{center}
\end{table}

% \begin{table}[h]
% \begin{center}
% \begin{minipage}{\textwidth}
% \caption{Data format for XGBoost regressor}\label{tab2}
% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
%       \toprule%
%       & \multicolumn{3}{@{}c@{}}{Tags as columns\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Tokens as columns\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
%       Track & rock &  \dots  & $\y_{valence}$ & $\position_{0} &  \dots $ & $\sigma_{valence}$ \\
%       \midrule
%       Element 3  & 100 &  \dots  & 0.563 & 780 A & 1166 & $1239\pm100$\\
%       Element 4  & 75  &  \dots  & 0.434 & 900 A & 1268 & $1092\pm40$\\
%       \botrule
%       \end{tabular*}
%       \footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
%       \footnotetext[1]{Example for a first table footnote.}
%       \footnotetext[2]{Example for a second table footnote.}
% \end{minipage}
% \end{center}
% \end{table}

@@

\bibliography{bibliography}% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl
